---
title: "Transition to HER - Sitka 2018 Forecast Notes"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(knitr)
library(tidyverse)
```

## Model definitions

LS:  ADFG's least squares model 

HAM:  Martell's model

HER:  ADFG's adaptation of HAM

## Objectives from Jane's workplan

HER (Martell’s age-structured herring model) for Sitka: 
1.  Update report file
2.  Generate graphics and tables
3.  Conduct retrospective analysis
4.  Add feature to examine likelihood profiles 
5.  Estimate variance using MCMC on *quantities of interest*
6.  Run simulation test
7.  Goal of a side-by-side comparison of 2018 forecast (2017 data)
    +  Document any differences in underlying model structure or assumptions
    +  Compare *quantities of interest* and explore differences

### What are the *quantities of interest* for variance:
~Mature biomass (pre-fishery)~
~~Spawning stock biomass (post-fishery)~~
~~Forecast mature biomass~~
~~Natural mortality/survival~~
Recruitment
Maturity
Selectivity
Catch - I added this, but it only works when conditioning on effort (conditioning on catch assumes zero variance)
*Egg deposition?*

### What are the *quantities of interest* for side-by-side:
Mature biomass (pre-fishery)
Spawning stock biomass (post-fishery)
Forecast mature biomass
Natural mortality
Recruitment
Maturity
Selectivity
Catch
Age compositions (residuals)
Egg depositions


## Work log and action items

### Meetings and individual hours worked

Sara and Jane Meeting 2018-04-10 0900-1200
Jane 2018-04-12 1400-1630 
Jane 2018-04-13 0800-1200
Sherri, Sara, Jane Meeting 2018-04-13 1330-1630
Jane 2018-04-16 0800-1200
Sherri, Sara, Jane Meeting 2018-05-10 1500-1615

### Jane to do (from 7/17 meeting)
1.  ~~Send Sherri PMRN literature.~~
2.  ~~Check with Siddeek on his experience and motivation for likelihood profiles. RESPONSE: He does this tediously by hand (outside of ADMB) and agrees that the posterior functionally replaces the likelihood profile approach.~~
3.  ~~Literature for why you would use likelihood profiles (vs posteriors); convergence, local minima, and estimating variance. RESPONSE: Emailed Ben and Sherri 2018-07-18 to ask likelihood profiles to be removed from my list of things to do, sent Ben Bolker's chapter on likelihoods as justification that this approach is not used for complex models.~~
4.  Goal of running longer chain over the weekend.


### Sherri to do before 5/30
1.  Why does the log standard error roughly equal the CV?
2.  Give Jane CVs from 2018 forecast model because 1978-1990 
    get updated from the regression.
3.  How did Steve get the CV for the 1971-1977 hydroaccoustic data?

### Jane to do before 5/30
1.  ~~Round fecundity regression coefficients to 1 decimal place.~~
2.  Selectivity blocks
3.  Commercial and spawning weight at age are the exact same except for 1997 (Sitka only!!). It is our best estimate of population waa

### Sherri to do before 5/10
1.  ~~Look into the variance/log se issue with the egg deposition data.~~
2.  ~~Precision/sig figs on fecundity regression coefficients. Also change in spawn dep data file.~~

### Jane to do between 5/10
1.  ~~Go back to time blocks for log mean M~~
2.  ~~List potential reasons why there are diffs between LS and HER~~ Added new section called "Model differences" to this file.
3.  ~~List changes to priors, provide justification~~ Added new section called "Priors" to this file.
4.  ~~Change precision on data (see Notes #4)~~
5.  Selectivity blocks

### Sherri to do before 4/13
1.  ~~Look into the variance/log se issue with the egg deposition data. *In progress.*~~

### Jane to do before 4/13
1.	~~Maturity time blocks – how to add more than one block (is the code structured the same as selectivity or natural mortality?)~~ Completed, but results for each time block has to be extracted individually in the REPORT section. Add to list of potential questions for Rudd or Martell. This parameter was also fixed instead of estimated in Steve's code.
2.	~~Phases: what does it mean when phase is -2? -1 means the parameter is fixed (not estimated), which also doesn’t make sense.~~ Any negative phase means the parameter is fixed instead of estimated in any particular phase (so -1 does the same thing as -2 or -5).
3.  ~~Time varying deviations on M.~~ Completed, changed prior on mean M to match BC. See justification in Priors section.

### For HER hash 4/13
1.  ~~Natural mortality estimation, including discussion of cubic spline (random walk?), priors on M, and how much the block deviations should vary between blocks~~ 
2.  ~~Precision of input data~~ except precision on fecundity coeffs still lingering

### For HER hash 5/10
1.	Forecast code in both models to make sure things are matching up
2.	Egg deposition variance. Where is this data and how did Steve calculate log standard error?
    + the log se ~= the CV, which we can get from the bootstrap
    + 1971-1977 is not from egg surveys, they are from hydroaccoustics
    + 1978-1990 is estimated from the regression of mean versus sd of 1991-present (and is recalculated annually)
    + in 2017 model
Other data and control file questions

## Notes
1.	Model fecundity
    +	~~Check to make sure model only estimates fecundity for 1980 on~~ They are.
    +	Fecundity regression coefficients for old model in Sitka.ctl, in sitka.dat data file for HER

2.	Catch
    +	~~upper 1990s had a different level of precision in HER model~~

3.	Model HER from 1980 on, but once transition over (after HER model updates and checks) then start the HER model at 1971. 
    +	With our least squares structure the small variance (high weight) on the low abundance years in the 1970's doesn't work well and Pete Hulson recommended from his work to start at 1980. In the HER structure, it should hopefully be stable enough and weighting different enough that 1971 start date shouldn't be a problem.

4.	~~Why there a high precision for catch (tons) and spawner weight at age and catch weight at age? Get rid of? Can we move to no decimal place precision or just one?~~
    + During HER hash 4/13 Sherri gave the following guidance on number of decimal points: 2 for catch, 1 for weight-at-age, 4 for age compositions, 6 for egg depositions

5.	Does ADMB read -9 differently than -9.000000? integer versus double?

6.	Egg deposition is in log space and se and not just variance
    +	Where is this data from?
    +	For 2016 and 2017, we used the variance from 2015 as a placeholder

7.	Mile days of milt
    +	~~How can we add in future?~~
    + This framework is functionally a duplicate for egg deposition, so potentially the weighting would be difficult. May be less of an issue with HER than LS.

8.	Initial values for Ricker model in HER model
    +	Recruitment compensation instead of Ricker parameterization in HER model (Mace and Doonan 1988 reference)-explanation in Martell et al. 2008 paper (different parameterization for Ricker)-recruitment compensation k (relative improvement in survival from egg to recruit as the SSB tends toward zero) (Goodyear 1980)
    +	Alpha and beta can be derived from model output to make sure starting values are similar in HER model
    +	Recruitment has 4 parameters (ro, r_bar, reck, rinit, precision)
    +	Needs work to determine if initial values reasonable

9.	Initial value for natural mortality in HER model in the control file
    +	p1 and p2 are the parameters for the prior distribution around the parameter

10.	  Forecast weight at age and forecast calculation
    +	Determining if HER and old model have same forecast estimation
    +	HER model uses commercial and spawner WAA while older model only uses spawner WAA (but may in a prior step use commercial WAA)
    +	In old model fw_a_a is spawner WAA (defined in control file) not commercial WAA but in HER model, directly from data file (last year in data file)

11.	  Time varying
    +	Maturity blocks
        +	Loop control file in old model- the breaks show the start year but in the HER model, the year is the terminal year
        +	On Jane’s list
        +	2018 forecast (1980-2014,	2015-2017)
    +	Selectivity blocks
        +	2018 forecast (1980-2017)
        +	Logistic; number one in HER model
    +	Natural Mortality blocks
        +	2018 forecast (1980-1998; 1999-2014; 2015-2017)

12.	  Other misc. section in ctl file
    +	Condition on catch for HER model to make similar to old model
    +	Check target harvest rate in HER model is 0.10????

13.	  Stopped at selectivity because question about phases 

Change in maturity curves after 2015. Potential mechanisms: population declines produce density-dependent response, where fish are maturing at an earlier age. Recent declines in size-at-age, potentially environmentally driven and coincident with recent warming temperatures (The Blob). The 2015 break was based on the shift in the PDO. 

## Model differences

A running log of potential reasons why the LS Model and HER do not match up.

1.   The structure and estimation of natural mortality is very different between models:  LS did not have any prior on M, only bounded from 0.001 to 1. LS estimates independent M for each time block. HAM/HER estimtes log mean M and then estimates time varying (block or cubic spline) deviations for each block. HAM estimation of natural mortality deviations turned off. Got them turned on, tested the cubic spline functionality, and changed the prior to be consistent with the BC stock assessment ISCAM (https://github.com/smartell/iSCAM/blob/IPHC/examples/BCHerring/DATA/SOGLN1/SOG2012.ctl).

2.   Rounding issues in the input data. The LS dat file had extremely high and unrealtistic precision.

3.   HER does not use objective function weights.

4.   Phasing different for leading parameters?

5.   HER did not have the pre-fishery mature biomass/numbers. 
## Priors

A list of priors, starting values, and bounds for each model, as well as justification for why any of these quantities were changed.

**Abbreviations/Terminology:**
Phase - phase in which parameter is estimate (-2 means parameter was fixed)
SV - starting value
LB/UP - lower and upper bound
p1/p2 - parameters for prior (normal has mu and sd, beta has alpha and beta, etc.)

```{r echo=FALSE}

kable(data.frame(Parameter = c("Block-specific M", "Log mean M", "Log mean M"),
           Model = c("LS", "HAM", "HER"),
           Phase = c("2", "2", "1"),
           SV = c("N/A", -1.05, -0.7985),
           Prior = c("N/A", "Unform", "Normal"),
           LB = c(0.001, -6.79, -5.00),
           UB = c(1.00, 1.00, 5.00),
           p1 = c("N/A", -1.05, "mu = -0.7985"),
           p2 = c("N/A", 0.05, "sd = 0.4")))

```

**Justification for changing prior on log mean M:** the uniform prior limitted how much we could increase the sd in natural mortality deviations. I used the normal prior parameters from ISCAM, which allowed the time varying deviations to vary more broadly.

## Lingering questions

+  What does the value() fxn do and when do you have to use it?
+  How do you get likelihood profiles for time-varing parameters?
+  If a parameter has both an upper bound and a lower bound, as well as parameters for a uniform prior, what are the actual bounds for estimation?
+  Extracting time varying maturity parameters in report file (currently hard-coded so you have to know how many blocks there are ahead of time).
+  When meeting with Kyle on herring data, review whether or not we want to round biomass (significant digits). Look also at other ASA models to see if they should be rounded.
+  Having a problem getting estimates for selectivity Sij. I don't understand Sij.sub(mod_syr,mod_nyr) = mfexp(log_slx);  I've tried the following lines but had no luck. 
  //Sij(mod_syr,mod_nyr) = mfexp(log_slx);
  //Sij(mod_syr,mod_nyr+1,sage,nage) = mfexp(log_slx);
  //Sij(mod_syr,mod_nyr,sage,nage) = mfexp(log_slx);
  //Sij = mfexp(log_slx);
  
## Future HER development

1.    Population dynamcis equations and assumptions related to maturity, selectivity, and weight-at-age:

+   Revisit how the spawning population is defined. Currently the LS and HER models define it as spawning numbers-at-age = (maturity matrix $\times$ numbers-at-age) – catch-at-age. Steve M. originally had it as maturity_matrix $\times$ (numbers-at-age - catch-at-age). Similarly, may want to revisit post fishery numbers-at-age (mature + immature) with is numbers-at-age - catch-at-age. Steve’s notation on how he calculates the spawning population is conflicting. The equation in the code (as you mention below) is (Nij-catch at age) $\times$ maturity, and that is how he describes it in his contract report (last paragraph page 14) and defines it in his contract equation T2.10 on page 27, but it does not match the note he put in the code which says that he coded it as in LS (maturity matrix*Nij)-catch-at-age per a contract between he and I. I’m wondering if added that note but never changed the code and report.

+   Revisit the question of how to treat selectivity. Do we apply selectivity to numbers-at-age as is done now in both HER and LS, such that it is essentially the combination of availability and fishery selectivity? Or do we change it so that numbers-at-age is first multiplied by maturity and then by selectivity (such that selectivity in this case is fishery selectivity alone and maturity deals with the fish that are available to the fishery on the spawning grounds)?

+  Currently spawner and fishery weight-at-age are identical (fishery is used for spawner weight-at-age in all years except 1997) - do we really feel like 1997 should be an exception? Also, why do we collect cast net weight-at-age if we don't use them? In PWS they take gonad condition to determine proportion mature.

+  We currently assume the spawning population has a 50:50 sex ratio. Do we have data to support this assumption or otherwise?

## HER variable definitions

### Model dimensions
$dat_syr$: first year of data
$day_nyr$: last year of data
$mod_syr$: first year of model
$mod_nyr$: last year of model
$sage$: first age class
$nage$: plus group age class
$rec_syr$: first year of recruitment (e.g. if mod_syr = 1971, rec_syr = 1974)
$h$: time blocks


### Controls for time varying parameters

Maturity
$nMatBlocks$: number of maturity blocks
$maturity\_cont$: matrix of maturity parameter controls (1,nMatBlocks,1,4)

Natural mortality rate deviations in each block
$mort\_type$: constant or interpolated using cubic spline
$mort\_dev_phz$: phase for estimating $M$
$nMortBlocks$: number of mortality blocks or nodes in the case of cubic spline
$nMortBlockYear$: terminal year of each mortality block (vector of length $nMortBlocks$)

Selectivity
$nSlxCols$: number of columns in selectivity design matrix (*FLAG - fixed at 9?*)
$nSlxBlks$: number of selectivity blocks/patterns 
$selex\_cont$: matrix of controls to be read in from control file.
$nSelType$: type of selectivity curve (currently only logistic), vector (1,$nSlxBlks$) 
$nslx_phz$: phase of estimation for each block, vector (1,$nSlxBlks$) 
$nslx_rows$: number of row for $log\_slx\_pars$, vector (1,$nSlxBlks$) 
$nslx_cols$: number of columns for $log\_slx\_pars$, vector (1,$nSlxBlks$)
$nslx_syr$: start year for each selectivity block, vector (1,$nSlxBlks$)
$nslx_nyr$: vector (1,nSlxBlks)
$log\_slx\_pars$: 

### Time series data
$data_catch$: catch in short tons (Year, Catch, log.se)
$data_sp_waa$: spawner weight-at-age in grams (Year, weight-at-age)
$data_cm_waa$: commercial catch weight-at-age in grams (Year, weight-at-age)
$data_cm_comp$: commercial catch composition (Year, age proporitons)
$data_sp_comp$: spawn sample age composition (Year, age proportions)
$data_egg_dep$: egg deposition survey in trillions of eggs (Year, Index, log.se)
$avg_sp_waa$: Average weight-at-age in grams of spawning biomass *FLAG - check the dimensions here*

### Population parameters
$log_natural_mortality$: mean natural mortality in log space (keeps estimate positive); theta(1)
$log_rinit$: log initial average age-3 recruitment for ages 3-8+ in dat_syr; theta(2)
$nFecBlocks$: number of fecundity blocks
$fec_slope$: slope of regression line in fecundity relationship
$fec_inter$: intercept of regression line in fecundity relationship

### Variables
$ro$: equilibrium recruitment
$reck$: recruitment compensation ratio

$so$: the 'alpha' parameter in the standard Ricker stock recruitment function
$beta$: the beta parameter in the standard Ricker function 
$$recruits=so*spawners*e^{-beta*spawners}$$
`fore`
$fore\_sb$: forecasted spawning biomass
$fore\_vb$: forecasted vulnerable biomass
$ghl$: guideline harvest level
$pyr$: forecast year ($mod_nyr$+1)
$fore\_rt$: ricker stock-recruit curve to forecast one year of recruitment
$fore\_nj$: abundance-at-age in forecast year
$pa$: 

### Vectors
~~$ssb$: spawning stock biomass at the time of spawning *FLAG - JYS got rid of this when I added the new mature and spawning population variables, replaced by $sp\_B$*~~
$recruits$: vector of $sage$ recruits predicted by S-R curve
$resd\_rec$: vector of residual process error (log-normal) (rec_syr,mod_nyr+1)
$pred\_egg\_dep$: model predicted egg deposition (mod_syr,mod_nyr)
$resd\_egg\_dep$: residual egg deposition (obs - pred) (mod_syr,mod_nyr)

$pred\_mileday$: model predicted mile days of milt *egg dep is derived from this so it's not currently used* (mod_syr,mod_nyr)
$resd\_mileday$: residual mile days(mod_syr,mod_nyr)
$pred\_catch$: predicted catch (mod_syr,mod_nyr)
$resd\_catch$: residual catch (mod_syr,mod_nyr)

$mbar$: average natural mortality
$mat\_bar$: average maturity
$wa$: extracted annual vector of commercial catch weight-at-age
$wbar$: average weight of catch

### Matrices 

Dimensions: ($mod\_syr$,$mod\_nyr+1$,$sage$,$nage$)

$Eij$: fecundity-at-age $j$ in year $i$
$Nij$: numbers-at-age 
~~$Oij$: mature numbers-at-age after fishery (spawning population) *FLAG - JYS got rid of this when I added the new mature and spawning population variables; now Oij = $sp\_Nij$*~~
$mat\_Nij$: matrix of pre-fishery mature numbers-at-age by year $i$
$mat\_Bij$: matrix of pre-fishery mature biomass-at-age by year $i$
$sp\_Nij$: matrix of post-fishery mature (spawning) numbers-at-age by year $i$
$sp\_Bij$: matrix of post-fishery mature (spawning) biomass-at-age by year $i$
$Pij$: numbers-at-age post harvest
$Sij$: selectivity-at-age
$Qij$: vulnerable proportions-at-age
$Cij$: predicted catch-at-age in numbers
$Mij$: natural mortality by age and year


$mat\_N$: vector pre-fishery mature total abundance by year $i$
$mat\_B$: vector of pre-fishery mature total biomass by year $i$
$sp\_N$: vector of post-fishery mature (spawning) total abundance by year $i$
$sp\_B$: vector of post-fishery mature (spawning) biomass by year $i$

$pred\_cm\_comp$: predicted commercial compositinos
$resd\_cm\_comp$: residual commercial compositions 
$pred\_sp\_comp$: predicted spawning composition 
$resd\_sp\_comp$: residual spawning composition 

## LS variable definitions

### Model dimensions

$nages$: number of ages
$dat\_styr$: data start year
$dat\_endyr$: data end year
$mod\_styr$: model start year
$mod\_endyr$: model end year
$dyrs$: data year index
$myrs$: model year index
$md\_offset$: offset data to model *FLAG - can you explain this?*
$Year$: year sequence for graphics (model + 1)
$i$: year
$j$: age
$t$: time block

### Phasing 

An interesting way to do this, not how HER is structured.

Phase 1:
$ph\_Int$: initial population
$ph\_S    $: natural mortality
$ph\_mat\_a$: maturity inflection
$ph\_gs\_a $: gear selectivity inflection
$ph\_gs\_b $: gear selectivity slope

Phase 2:
$ph\_mat\_b$: maturity slope

Phase 3:
$ph\_Rec$: recruitment (age-3)
$ph\_Ric$: Ricker function

### Data

$tcb$: total annual commercial catch (short tons)
$tcbm$: $tcb$ in metric tons (metric tons = 0.90718 * short tons)
$obs\_sp\_waa$: spawning (cast net) weight-at-age
$obs\_c\_waa$: commercial catch weight-at-age
$obs\_c\_comp$: commercial catch age composition
$obs\_sp\_comp$: spawner (cast net) age composition
$obs\_egg$: egg deposition
$mile\_days$: mile days of milt (not always used)

### Time blocks

Written this way to accomodate blocks and looping. Not necessarily recommended for HER.

$S\_Bk$: number of survival blocks (1 split = 2 blocks) *FLAG - this is incorrectly defined as $M\_Bk$ in LS tpl documentaiton* 
$S\_Bk\_Yrs$: specific years in which survival $S$ changes *FLAG - this is incorrectly defined as $M\_Bk\_Yrs$ in LS tpl documentaiton* 
$mat\_Bk$: number of maturity blocks (1 split = 2 blocks)
$mat\_Bk\_Yrs$: specific years in which maturity-at-age changes
$gs\_Bk$: number of gear selectivity blocks (1 split = 2 blocks)
$gs\_Bk\_Yrs$: specific years in which gear-selectivity-at-age changes
$F\_Bk$: number of fecundity blocks (1 split = 2 blocks)
$F\_Bk\_Yrs$: specific years in which fecundity changes
$F\_slope$: Slope of fecundity-at-age regression
$F\_inter$: Intercept of fecundity

### Parameters

Initialize population
$init\_age_3$: vector of initial age-3 abundance by year
$init\_pop$: vector of initial population abundance (ages 4 - 8+)

Spawner-recruit relationship
$log\_alpha$: natural log-scale spawner-recruit alpha parameter (estimate)
$log\_beta$: natural log-scale spawner-recruit beta parameter (estimated)
$alpha$: spawner-recruit alpha parameter (derived)
$beta$: spawner-recruit beta parameter (derived)

Natural mortality and survival
$M$: natural mortality
$Sur$: survival matrix (i, j) *FLAG - is this here for age-dependent survival?*
$S$: survival vector (1:$S\_Bk$)
$S\_for$: mean survival (for forecasting) *FLAG - incorrectly defined in LS tpl documentation. This is not mean survival, it's the most recent survival -> Sur(myrs,1)*
  
Maturity
$mat\_a$: age at 50% maturity
$mat\_b$: maturity-at-age slope
$Mat$: Maturity-at-age matrix (1,myrs,1,nages)
$mat\_for$: *FLAG CHECK* forecast maturity-at-age -> the most recent year maturity-at-age. *This variable does not actually get used in forecast*

Selectivity
$gs\_a$: age at 50% selectivity
$gs\_b$: selecitivity-at-age slope
$GS$: *FLAG CHECK* gear selectivity-at-age matrix (1,myrs,1,nages)
$GS\_Sc$: *FLAG CHECK* scaled gear selectivity-at-age matrix
$int1$: maximum of gear selectivity, used to scale
$int2$: *FLAG - what is pop rec* proportion of pop rec to gear \times weight-at-age *FLAG - proposed defn:* proportion vulnerable-at-age \times commercial weight-at-age
$int3$: int2 summed over ages (one for each year $i$)

Mile days of milt
$md\_c$: mile-days coefficient *FLAG - what's this? we do not have anything similar in HER*

### Matrices
$naa$: total population (mature + immature) (millions)
$sel\_naa$: *FLAG* Current defn: N selected by gear. Improved defn: numbers-at-age vulnerable to gear
$sel\_naa\_prop$: *FLAG* Current definition: proportion of N selected by gear. Improved defn: proportion vulnerable-at-age (out of the vulnerable population)
$est\_c\_naa$: catch composition-at-age                                  
$est\_sp\_naa$: spawning numbers-at-age (millions)            
$est\_sp\_comp$: spawners numbers-at-age (proportion)            
$est\_sp\_baa$: spawning biomass-at-age (metric tons)
$est\_mat\_naa$: mature abundance-at-age (millions)                       
$est\_mat\_baa$: mature biomass-at-age (metric tons)          
$post\_naa$: numbers-at-age post-harvest; total numbers-at-age (mature + immature) - catch (millions)     
$est\_egg\_naa$: egg production-at-age (trillions) (egg deposition)    

### Vectors
$tot\_sel\_N$: total N selected by gear (millions)                      
$tot\_sp\_B$: total spawning biomass (metric tons)
$tot\_mat\_N$: total mature abundance (millions)
$tot\_sp\_N$: total spawning abundance (millions)                    
$tot\_mat\_B$: total mature biomass (metric tons)   
$tot\_post\_N$: total population (mature + immature) - catch (millions)     
$tot\_est\_egg$: total egg deposition (trillions)                          
$N$: total abundance (mature + immature) (millions)
$SR$: Ricker spawner-recruit
$M_D$: Mile days of milt


### Forecast quantities
$for\_naa$: forecast numbers-at-age (mature + immature) (millions)
$for\_mat\_naa$: forecast mature numbers-at-age (millions)
$for\_mat\_baa$: forecast mature biomass-at-age (metric tons)
$for\_mat\_prop$: forecast mature proportion-at-age by number
$for\_mat\_\b_\prop$: forecast mature proportion-at-age by biomass
$for\_mat\_B$: total forecast mature biomass (metric tons)
$for\_mat\_B\_st$: total forecast mature biomass (US short tons) 
$for\_tot\_mat\_N$: total mature numbers-at-age                   
$HR$: harvest rate                                 
$HR\_p$: harvest rate sliding proportion               
$GHL$: guideline harvest limit       
$fw\_a\_a$: forecast weight-at-age, most recent year of spawner weight-at-age. Commented out in tpl, now defined in tpl.

### Objective function components

$res\_c\_comp$: residuals catch age composition      
$res\_sp\_comp$: residuals spawner age composition
$res\_tot\_egg$: residuals egg deposition
$res\_SR$: residuals spawner-recruit function
$SSQc$: Sums of squares catch age composition
$SSQsp$: Sums of squares spawner age composition
$wSSQE$: Sums of squares weighted egg deposition vector over years
$WSSQE$: Sums of squares egg deposition
$SSQR$: Sums of squares spawner-recruit
$M_DR$: *FLAG CHECK* Sums of squares mile-days of milt vector over years
$wSSQM$: *FLAG - what's this?*
$WSSQM$ *FLAG - what's this*

### Objective function weights

HER does not have objective function weights

$lC$: Catch age composition (number)
$lS$: Spawning age composition (number)
$lR$: Ricker spawner-recruit (number)
$lD$: Egg Deposition (btw dataset weighting) (number)
$lE$: Egg deposition (within) (vector of years)
$lM$: Mile-days (vector of years)

### Bootsrap and SD report calls

Bootstrap has not been implemented (at least since 2015)

$BSDATA$: Define bootstrap data matrix (1,myrs,1,26)
$Data_start_year$: Index number
$Data_end_year$: Index number
$Model_start_year$: Index number
$Model_end_year$: Index number
$obj$: Rejection criteria number

SD report calls

$SpawnBio$: Spawning biomass (vector 1,myrs)
$SpawnBioFor$: Forecast spawning biomass (number)
$GHLsd$: GHL (number)
$AICcsd$: AIC (number)
